The Driving Forces Behind API Evolution

### 2015-05-20 thesis/paper.tex
Improved importance for case company

%Purpose of the study
The goal of the study was twofold. Firstly, the aim was to explore what are the driving forces behind API evolution and secondly, to validate the results' level of correctness by comparing our findings with the case company's explanation of the changes. With this information, we could determine to what extent these change decisions can be reverse engineered. 
%Why this is important for the case company.
Understanding what drives the evolution of their API could be significant value to the case company. Being aware of what types of changes occur more frequently can help the case company design their APIs to mitigate or assist these types of change. Furthermore, understanding which software evolution theories apply to APIs can help the case company control the evolution of their API and could help them better prepare for change in the future.

>>>>

%Purpose of the study
The goal of the study was twofold. Firstly, the aim was to explore what are the driving forces behind API evolution and secondly, to validate the results' level of correctness by comparing our findings with the case company's explanation of the changes. With this information, we could determine to what extent these change decisions can be reverse engineered. 
%Why this is important for the case company.
This study has many potential benefits for the case company. Identifying the types of changes that occur when an API evolves will improve communication and discussions regarding maintenance and evolution tasks. This improved communication could provide a common language that developers, users and management can use to discuss potential evolution of the APIs. Understanding the evolution theories could further assist understanding of how change will occur and how to plan for it. Lastly, by keeping a history of changes to an API over time, trends can be identified which could help with future API design.
